### 2022-03-15 omicron-generation.tex
micro edit
update output

Serial interval data are taken from the supplementary material of \cite{backer2021omicron}.
The data are aggregated by the length of the serial interval in days and do not include additional individual-level information, such as exposure dates or symptom onset dates.
The data consists of 2529 transmission pairs and are further stratified by the presence of S gene target failure (SGTF), week of infectors' symptom onset date (weeks 50 and 51), and the type of transmission (within or between households).
In the main text, we combine data from weeks 50 and 51 and instead present a stratified analysis in Supplementary Material.
For simplicity, we refer to transmission pairs with and without S gene target failure as Omicron and Delta transmission pairs, respectively.
Incubation period data are not publicly available with the original article; instead, we rely on previously-estimated incubation-period distributions by \cite{backer2021omicron} to derive growth-rate-adjusted .
See original article for details of data collection.

>>>>

Serial interval data are taken from the supplementary material of \cite{backer2021omicron}.
The data are aggregated by the length of the serial interval in days and do not include additional individual-level information, such as exposure dates or symptom onset dates.
The data consists of 2529 transmission pairs and are further stratified by the presence of S gene target failure (SGTF), week of infectors' symptom onset date (weeks 50 and 51), and the type of transmission (within or between households).
In the main text, we combine data from weeks 50 and 51 and instead present a stratified analysis in Supplementary Material.
For simplicity, we refer to transmission pairs with and without SGTFs as Omicron and Delta transmission pairs, respectively.
Incubation period data are not publicly available with the original article; instead, we rely on previous estimates by \cite{backer2021omicron} to derive growth-rate-adjusted incubation-period distributions.
See original article for details of data collection.
